### 2021-10-01 README.Rmd
Update README

This package is designed to work for spatially mapped, repeat censused forests plots. The package has commands to fit models of tree growth based on neighborhood competition which can be used to estimate species-specific competition coefficients. The model fits can then be evaluated using a spatial cross-validation scheme to detect possible overfitting. Additionally, these models can test whether the species identity of competitors matters using a permutation test-style shuffling of competitor identity (under the null hypothesis) and subsequently evaluating if model performance changes. See Allen and Kim (2020) [A permutation test and spatial cross-validation approach to assess models of interspecific competition between trees](https://doi.org/10.1371/journal.pone.0229930) for a full description.

>>>>

This package is designed to work for spatially mapped, repeat censused forests plots. The package has commands to fit models of tree growth based on neighborhood competition which can be used to estimate species-specific competition coefficients. The model fits can then be evaluated using a spatial cross-validation scheme to detect possible overfitting. Additionally, these models can test whether the species identity of competitors matters using a permutation test-style shuffling of competitor identity (under the null hypothesis) and subsequently evaluating if model performance changes. See Kim et al. (2021) [The `forestecology` R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees](http://doi.org/10.1002/ece3.8129) for a full description.
